---
title: Deploying cross-language in high impact projects
---


The materials here support a talk at the [Spatial Data Science across Languages (SDSL)](https://spatial-data-science.github.io/2024/) conference 2024.

See the [slides here](slides) and in the dropdown menu above.

The quickest way to reproduce the code is probably with GitHub codespaces, by opening the following link.

[![Open in GitHub Codespaces](https://github.com/codespaces/badge.svg)](https://codespaces.new/Robinlovelace/cross_language_projects)

See the source code at [github.com/robinlovelace](https://github.com/Robinlovelace/cross_language_projects).

See the README for more information.

Based on https://robinlovelace.github.io/reproducible-slides-repo-template/slides 

To create your own "reproducible slides repo" follow the instructions in the link above, starting by cloning this repo or creating a template from this one: 

```bash
gh repo clone robinlovelace/cross_language_projects
code cross_language_projects
```

Or go to https://github.com/Robinlovelace/reproducible-slides-repo-template and click "Use this template".

## Setup

To setup the repo the following commands were used

```bash
gh repo create # create the repo on github
```

```{r}
#| eval: false
# Take snapshot with renv:
renv::snapshot()
```

Load the renv with this (also in .Rprofile):

```{r}
source("renv/activate.R")
```

```{r}
# make renv pick-up rmarkdown dep:
library(rmarkdown)
library(knitr)
```

Install Python packages with:

```{r}
# reticulate::install_python()
reticulate::py_install("geopandas")
```