---
title: Deploying cross-language in high impact projects
---

The materials here support a talk at the [Spatial Data Science across Languages (SDSL)](https://spatial-data-science.github.io/2024/) conference 2024.

See the [slides here](slides) and in the dropdown menu above.

The quickest way to reproduce the code is probably with GitHub codespaces, by opening the following link.

[![Open in GitHub Codespaces](https://github.com/codespaces/badge.svg)](https://codespaces.new/Robinlovelace/cross_language_projects)

See the source code at [github.com/robinlovelace](https://github.com/Robinlovelace/cross_language_projects).

See the README for more information.

Based on https://robinlovelace.github.io/reproducible-slides-repo-template/slides 

To create your own "reproducible slides repo" follow the instructions in the link above, starting by cloning this repo or creating a template from this one: 

```bash
gh repo clone robinlovelace/cross_language_projects
code cross_language_projects
```

Or go to https://github.com/Robinlovelace/reproducible-slides-repo-template and click "Use this template".

## Setup

To setup the repo the following commands were used

```bash
gh repo create # create the repo on github
```

```{r}
#| eval: false
# Install R dependencies:
remotes::install_github("robinlovelace/cross_language_projects")
```

Install Python and necessary Python packages if not already installed with:

```{r}
#| eval: false
reticulate::install_python()
```

```{r}
reticulate::py_install("geopandas")
reticulate::py_install("matplotlib")
```

Install Julia if not already installed:


```bash
curl -fsSL https://install.julialang.org | sh
```

Activate the Julia environment:

```julia
using Pkg
Pkg.activate(".")
Pkg.status()
```
